\chapter*{Terms of Reference}

\section*{Project title}
Neural Networks with Python and TensorFlow

\section*{Stakeholders}
Alexander James Johnson (Student),\\
Dr Stephen Lynch (Project supervisor).

\section*{Project Background}
Artificial Intelligence (AI) still remains as one of the greatest challenges in
scientific research to this date, but much progress in the field has been made
using artificial neural networks.
The design of artificial neural networks is loosely inspired by that of
biological brains, and serves as an expansion of an earlier concept called the
perceptron \citep{Rosenblatt:1958:Perceptron}.
By using multiple layers of these artificial neurons, we can form a highly
connected system that is referred to as a neural network,
these networks can then be trained on a large data set to predict the output
with high accuracy.

The range applications for neural networks is wide: they can be used to classify
data, predict future states of chaotic systems, apply stylisations to images,
and control physical/physically-based system in real-time.

\section*{Aims}
\begin{itemize}
    \item Provide introductory information about neural networks and TensorFlow
        suitable for those without prior knowledge in the field.

    \item Produce a neural network model to reliably solve an advanced problem,
        potentially related to robotics.
\end{itemize}
\newpage
\section*{Objectives}
Listed here are a set of objectives, and a suggested date for their completion\\
given as [year/month/day].
\begin{itemize}
    \item Reproduce results previously obtained in MATLAB using Python.
        [2020/02/01]

    \item Terms of reference submission. [2020/02/01]

    \item Use TensorFlow to produce results, giving a brief overview of how the
        TensorFlow library works, and how to use it. [2020/02/15]

    \item Background of a more advanced subject that will be the main focus of
        the report. [2020/03/10]

    \item Precursory results from own research. [2020/03/20]

    \item Preliminary report submission. [2020/03/27]

    \item Obtain sufficient results for own research. [2020/04/15]

    \item Completed own research, ready to begin final tweaks. [2020/05/10]

    \item Oral and poster presentations. [2020/05/21]

    \item Project submission. [2020/05/26]
\end{itemize}

\section*{Project Deliverables}
\begin{itemize}
    \item A selection of programs that perform the calculations.

    \item A report, providing details of the mathematics and methodologies used.

    \item An interim report, which will act as a self contained sample of the
        full report.

    \item A poster presentation, highlighting key aspects of the project and
        displaying relevant results.

    \item An oral presentation, providing an in-depth overview of the report.

    \item A terms of reference document, describing the scope and purpose of the
        project (this document).
\end{itemize}

\section*{Required Resources}
\begin{itemize}
    \item Access to hardware capable of running Python and TensorFlow.

    \item Access to library and internet resources, for research purposes.

    \item An implementation of \LaTeX, for report writing.
\end{itemize}
All of the above requirements are already satisfied by the University or
otherwise.
